Hierarchical Control for Aircraft Electronic Power Systems

### 2012-12-07 project/report/paper.tex
added example priority table (straight from Mehdi's paper. will modify it later)

[TODO: show priority tables]

>>>>

[TODO: show priority tables; numerical example]

\begin{table}[t]
\caption{Load Priority Table Example} %from Mehdi's paper
\label{T:shed} 
\centering
\begin{tabular}{c|cc}
 Non-sheddable loads (W) & Sheddable loads (W) & Shed priority \\ \hline
1000 & 1000 & 1 \\
1000 & 5000 & 2 \\
500 & 2000 & 3 \\
5000 & 2000 & 4 \\
1000 & 1000 & 5 \\
1000 & 5000 & 6 \\
2000 & 1000 & 7 \\
5000 & 2000 & 8 \\
500 & 2000 & 9 \\
2000 & 1000 & 10 \\ \hline
\end{tabular}
\end{table}
